---
title: 'Course: Data Science'
author:
- Anna Baghumyan
- Maria Davoodian
- Hermine Grigoryan
- Arusyak Hakobyan
- Lilia Mamikonyan
date: "July 19, 2018"
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning=F)
```

This is the continuation of text mining.

```{r, include=F}
library(dplyr) #Data manipulation (also included in the tidyverse package)
library(tidytext) #Text mining
library(tidyr) #Spread, separate, unite, text mining (also included in the tidyverse package)
library(widyr) #Use for pairwise correlation

#Visualizations!
library(ggplot2) #Visualizations (also included in the tidyverse package)
library(ggrepel) #`geom_label_repel`
library(gridExtra) #`grid.arrange()` for multi-graphs
library(knitr) #Create nicely formatted output tables
library(kableExtra) #Create nicely formatted output tables
library(formattable) #For the color_tile function
library(circlize) #Visualizations - chord diagram
library(memery) #Memes - images with plots
#library(magick) #Memes - images with plots (image_read)
library(yarrr)  #Pirate plot
library(radarchart) #Visualizations
library(igraph) #ngram network diagrams
#library(ggraph) #ngram network diagrams
```

```{r, include=F}
#Customize the text tables for consistency using HTML formatting
my_kable_styling <- function(dat, caption) {
  kable(dat, "html", escape = FALSE, caption = caption) %>%
    kable_styling(bootstrap_options = c("striped", "condensed", "bordered"),
                  full_width = FALSE)
}

aqua_data <- read.csv('aquaman.csv',  stringsAsFactors = F)
beasts<-read.csv("Beasts.csv", stringsAsFactors = F)

beasts$type<-c("beast")
aqua_data$type<-type<-c("aqua")
new_movies<-rbind(beasts, aqua_data[1:1400,])
glimpse(new_movies) #Transposed version of `print()`
```

```{r, include=F}
#Create tidy text format: Unnested, Unsummarized, Stop and Short words
new_tidy <- new_movies %>%
  unnest_tokens(word, Reviews) %>% #Break the reviews into individual words
  filter(!nchar(word) < 3) %>% #Words like "ah" or "oo" used in music
  anti_join(stop_words) #Data provided by the tidytext package
glimpse(new_tidy) #From `dplyr`, better than `str()`.

new_sentiments <- sentiments %>% #From the tidytext package
  filter(lexicon != "loughran") %>% #Remove the finance lexicon
  mutate( sentiment = ifelse(lexicon == "AFINN" & score >= 0, "positive",
                             ifelse(lexicon == "AFINN" & score < 0,
                                    "negative", sentiment))) %>%
  group_by(lexicon) %>%
  mutate(words_in_lexicon = n_distinct(word)) %>%
  ungroup()
```

```{r}
new_sentiments %>%
  group_by(lexicon, sentiment, words_in_lexicon) %>%
  summarise(distinct_words = n_distinct(word)) %>%
  ungroup() %>%
  spread(sentiment, distinct_words) %>%
  mutate(lexicon = color_tile("lightblue", "lightblue")(lexicon),
         words_in_lexicon = color_bar("lightpink")(words_in_lexicon)) %>%
  my_kable_styling(caption = "Word Counts Per Lexicon")
```
The table above gives an idea of the size and structure of each lexicon(library built in), which we will use in further analysis.

```{r, include=F}
movie_bing <- new_tidy %>%
  inner_join(get_sentiments("bing"))
movie_nrc <- new_tidy %>%
  inner_join(get_sentiments("nrc"))
movie_sub <- new_tidy %>%
  inner_join(get_sentiments("nrc")) %>%
  filter(!sentiment %in% c("positive", "negative"))
```

```{r}
new_plot <- movie_nrc %>%
  group_by(sentiment, type) %>%
  summarise(word_count = n()) %>%
  ungroup() %>%
  mutate(sentiment = reorder(sentiment, word_count)) %>%
  #Use `fill = -word_count` to make the larger bars darker
  ggplot(aes(sentiment, word_count, fill = -word_count)) +
  geom_col() +
  guides(fill = FALSE) + #Turn off the legend
  labs(x = NULL, y = "Word Count") +
  scale_y_continuous(limits = c(0, 1000)) + #Hard code the axis limit
  ggtitle("Beast And Aquaman Sentiment") +
  coord_flip()

plot(new_plot)
```

This plot shows the sentiment of two movies together and highlights the one with leading word count.
As we can see there are lots of positive sentiments, however, different types of negative ones
such as fear, anger, sadness, disgust are displayed seperately and combined could make a huge differnece.

```{r}
movie_polarity_type <- movie_bing %>%
  count(sentiment, type) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(polarity = positive - negative,
         percent_positive = positive / (positive + negative) * 100)

#Polarity by type
plot1 <- movie_polarity_type %>%
  ggplot( aes(type, polarity, fill = type)) +
  geom_col() +
  geom_hline(yintercept = 0, color = "red") +
  theme(plot.title = element_text(size = 11)) +
  xlab(NULL) + ylab(NULL) +
  ggtitle("Polarity By Type")

#Percent positive by type
plot2 <- movie_polarity_type %>%
  ggplot( aes(type, percent_positive, fill = type)) +
  geom_col() +
  geom_hline(yintercept = 0, color = "red") +
  theme(plot.title = element_text(size = 11)) +
  xlab(NULL) + ylab(NULL) +
  ggtitle("Percent Positive By Type")

grid.arrange(plot1, plot2, ncol = 2)
```

These two plots show the polarity and the percent positive by movie "type" (Aquaman or Beasts).
Polarity (positive - negative) field and a percent_positive field (positive/totalsentiment∗100) are ploted for different perspectives.
We can say that even though Aquaman has less postitive reviews then Beasts, when taking
into account all reviews the result is changing and the huge difference between the movies is
dissaperaing.
```{r}
#Get the count of words per sentiment per type
type_sentiment_nrc <- movie_sub %>%
  group_by(type, sentiment) %>%
  count(type, sentiment) %>%
  select(type, sentiment, sentiment_type_count = n)

#Get the total count of sentiment words per type (not distinct)
total_sentiment_type <- movie_sub %>%
  count(type) %>%
  select(type, type_total = n)

#Join the two and create a percent field
type_radar_chart <- type_sentiment_nrc %>%
  inner_join(total_sentiment_type, by = "type") %>%
  mutate(percent = sentiment_type_count / type_total * 100 ) %>%
  filter(type %in% c("aqua","beast")) %>%
  select(-sentiment_type_count, -type_total) %>%
  spread(type, percent)

chartJSRadar(showToolTipLabel = TRUE, scores = type_radar_chart,
             main = "Aqaman & Beasts Radar")
```
The radar shows that both movies have left similar patterns, however, there is more 
anger towards Beasts and  more joy towards Aqaman. So, we can conclude that by written reviews 
people have more positive views about Aquaman rather than Beasts.

